### 2017-10-10 response/response-jde-1.tex

Even with family fixed effects, crop loss is potentially tied with
omitted variables. Crop loss is subjectively measured, so we'd need to
rely on the claim of the survey respondent that the loss was for
"uncontrollable" circumstances. The use of family fixed effects does
address fixed differences in wealth or education that might be related
to families at greater risk of crop loss. But, there could still be time
varying factors. We can't be certain that the crop loss is not the
result of some disease epidemic (or conflict) that also could affect
fertility.

Suggestion: The manuscript should be a little more forthcoming about
this potential problem. I would like to see an exploration into the
potential mechanisms behind the crop loss. Is it weather?

[RESPONSE:]

% [see response to R1's q7 on time-varying covariates]
% 
% [TK we need to tone down the causality part; explain the growing season and
% the crop loss question]

% The question ask (Question 11.B.9): ``Have you lost any part of the 
% harvested crop to insects, rodents, fire, rotting, etc.?''
It is correct that the crop loss is subjectively measured and that
it is not possible to verify what factors played a role in the crop loss.
We have therefore reduced the use of causal language as detailed in our
response to Reviewer 1 above.

As you suggest, weather is a potential factor.
Unfortunately the only available weather data consist of monthly rainfall 
at district level (there are five districts in the data) with missing 
information for some months.
Furthermore, there is no 30 year average to compare the observed 
district level rainfall data to.
This means that it is not possible to reliably separate out positive 
(above mean) and negative (below mean) rainfall shocks.
Although community or women fixed effects will partly ameliorate the
problem of missing average data, we cannot rule out the possibility
that all observed periods deviated substantially from the average in 
the same direction in which case we will fail to capture that the observed
rainfalls were all ``shocks''.

@@

A number of different specifications of rainfall's association with 
crop loss is possible.
Kagera has two growing seasons, February through May and
October through December \citep[p 6]{Tanzania2007}.
We tried two different strategies: 
one where rainfall is measured as the average monthly rainfall 
over a set period prior to the survey month; 
and one based on average rainfall for growing season(s) preceding 
the survey month 
(that is, not including the current growing season if the survey
took place during a growing season).
Despite that rainfall is measured at district level either strategy
lead to variation across communities because of differences in 
when each community was surveyed.

The first strategy did not provide any clear results for a variety
of period lengths and we therefore focus on the growing season approach.
Appendix Table A-15 shows individual level fixed effects estimates of the 
effects of average monthly rainfall in centimeters on the likelihood
of experiencing a crop loss.
We use two specification, one with the last prior growing season and 
one with prior growing for waves 2 through 4 and the last two prior 
growing seasons for wave 1.
Higher rainfall is associated with a lower likelihood of a crop loss. 
A one standard deviation change in rainfall is associated with an
approximately 6 percentage point change in the probability of 
experiencing a crop loss.
We also tried adding square terms, but the estimated coefficients
were small and far from statistically significant.
The same is the case for using crop loss per capita as the dependent
variable.

### 2017-10-10 response/response-jde-1.tex

Suggestion: Control for family characteristics (age, proxies for
education, proxies for wealth) at the first wave interacted with survey
wave. At the very least, this will help acknowledge the identification
threat for the reader.

[RESPONSE:]

It is, indeed, potentially concerning that there are so substantial
differences in the proportion of households that experienced a 
shocks over the different rounds, although it is possible that
this simply is a stark reminder of the volatile nature of life
in a developing country.

We have added Appendix Table A-13 to address this
concern and discuss the results in the Robustness section. 
In addition to your suggestion of interacting a linear
time trend with wave 1 characteristics (assets per capita,
age group dummies, and education group dummies), we also present
a separate model where wave dummies are interacted with the
same set of wave 1 characteristics.
The small differences in point estimate and level of significance 
indicate that our results are not driven by differential trends
in which types of households that experience crop loss.

@@

Neighbors may be affected an individuals crop loss. For one, price of
food goes up. This could be a positive income shock for families with
crops, but bad for families working in other areas.

Suggestion: Aggregate crop loss to the community level and use that as
the treatment variable.

[RESPONSE:]

We already include a version of this in the paper, but the 
results were not well explained.
Appendix Table A-16 include the fraction of households in the community 
who have experienced a crop loss (excluding the household itself).
The sign of the village level crop loss are generally the same as
those for the household crop loss, although---with the exception
of traditional contraceptives---the village level variable is not
statistically significant.
Furthermore, the crop loss coefficients decline only slightly
when including village level crop loss indicating that there is
only relatively mild spill-over between households for this
particular type of shock.

Finally, as detailed in our response to Reviewer 1 on potentially 
time-varying covariates we specifically discuss that prices do not appear 
to have any association with fertility decisions and including 
a price index does not the change the main results.
